---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mileg

<!-- badges: start -->
<!-- badges: end -->

The goal of mileg is to offer anyone interested in Michigan politics a convenient way of *programmatically* accessing data on the Mi(chigan) Leg(islature). The programmatic piece is important: the tools here are geared first towards researchers, who often find themselves in a position of needing to compile and reformat data from, \*checks notes\*, *inconvenient* sources before incorporating it into their project or analysis. The structure of the package, however, could also be useful for folks in the policy space, who may want to use the database for bill tracking or other reporting.

For casual onlookers, the Legislature's public website is likely more than enough, but everyone is welcome to explore this resource for fun. As with anything in R, the open-source and free nature of the project is also hopefully appealing, given the often unreasonable price tags or other barriers to entry associated with using proprietary APIs or programs. So there's that, too.

## Installation

You can install mileg from [GitHub](https://github.com/) with:

```{r install, eval=FALSE, message=FALSE}
# install.packages("devtools")
devtools::install_github("aaronameek/mileg")
```

## Setup & General Use

In general, the dual goals of package-ifying this project was to make it both straightforward and flexible -- that is, every `R` user knows *how* to use a package, but they all have different use *cases*. For example, a user could run this brief chunk and end up with a fully-functional local database with 20 years worth of legislative data within a few minutes:

```{r setup_example, eval=FALSE, message=FALSE}
## Load main package (and friends)
library(mileg)
library(readr)
library(here)

## Fetch bill data
fetch_bill_data()

## Compile into database
bill_db_main(
  db_path = here("legislation.db"),
  previous_bills_df = read_csv("data/clean/clean_previous_bills.csv"),
  current_bills_df = read_csv("data/clean/clean_current_bills.csv"))
)
```

*This package is in active development. Apologies for any bugs, deficiencies, or wild updates as I work out the kinks!*
